### 2012-01-31 docs/notes.tex
Organizing and cleaning

\section{Simulation}
\begin{figure}
\center
\includegraphics[width=1.5in]{../figs/syn/mat.pdf}
\includegraphics[width=2.5in]{../figs/syn/counts.pdf}
\includegraphics[width=2in]{../figs/syn/bias.pdf}
\caption{Illustration of 1000 simulated events, as described in text. Left: Counts of each dyad. Center: Boxplot of distribution of participation counts across dyads.  The top left shows an increased propensity for reciprocity within cluster 1; bottom right shows more AB-AY events within cluster 2. Right: Loglikelihood vs. iteration during MCMC.}
\label{fig:syncounts}
\end{figure}

@@

\subsection*{Prediction experiment}
\begin{figure}
\center
\includegraphics[width=3.5in]{../figs/syn/test-recall.pdf}
\caption{Predictive performance on test data.  Left: Recall on synthetic example shown in Figure \ref{fig:syncounts}.}
\label{fig:recall}
\end{figure}
We evaluate the predictive ability of the learned models by comparing models based on the loglikelihood of held-out data and recall on held out data.  Each data set is first split into a training set and a test set, and the loglikelihood of the test set is computed using Equation \ref{eqn:llk} where $\beta$ is set to be the posterior mean given the training data.  Recall at a given cutoff $k$ is found by first sorting the predicted intensity functions at each time, then computing the mean rank of the observed events in that list.

>>>>

\section{Simulation}
\begin{figure}
\center
\includegraphics[width=2in]{../figs/syn/mat.pdf}
\includegraphics[width=3in]{../figs/syn/counts.pdf}
\caption{Illustration of 1000 simulated events, as described in text. Left: Counts of each dyad. Right: Boxplot of distribution of participation counts across dyads.  The top left shows an increased propensity for reciprocity within cluster 1; bottom right shows more AB-AY events within cluster 2.}
\label{fig:syncounts}
\end{figure}

@@

\subsection*{Prediction experiment}

\begin{figure}
\center
\includegraphics[width=3in]{../figs/syn/logposterior.pdf}
\includegraphics[width=3in]{../figs/syn/test-recall.pdf}
\caption{Results from fitting models to synthetic data. Left: Log posterior of 1000 simulated events vs. iteration during MCMC.  Right: Recall on 3000 test events.}
\label{fig:synresults}
\end{figure}
We evaluate the predictive ability of the learned models by comparing models based on the loglikelihood of held-out data and recall on held out data.  Each data set is first split into a training set and a test set, and the loglikelihood of the test set is computed using Equation \ref{eqn:llk} where $\beta$ is set to be the posterior mean given the training data.  Recall at a given cutoff $k$ is found by first sorting the predicted intensity functions at each time, then computing the mean rank of the observed events in that list.
